Fundamental Problems with the Evidence Base of Adolescent Depression Treatments

### 2024-03-27 Untitled.qmd
Cleaned and read in data from additional trials from systematic review

---
title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
author: "Stringaris et al"
prefer-html: true
format: docx
editor: visual
bibliography: "emotion_concepts_paper.bib"
font:
  family: "Calibri"
---

@@

```
# Introduction

@@

This assumption may be hard to meet. Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self- %\>% ion bias with respect to who participates in psychotherapy versus medication trials. Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity. Some of these characteristics, particularly baseline severity, may moderate treatment response (ref) and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.

@@

An inter-related issue concerns the nature of control interventions being used. Control conditions in trials are meant to generate counterfactual conditions (CITE RUBIN et al) to the intervention: what would have been the outcome in an individual had they not received the intervention. This implies that there is a latent distribution of values that represent that counterfactual condition which control arms in trials are meant to approximate. Those latent values of the counterfactual condition should, on average, not be different between psychotherapy and medication trials, provided that the samples are representative of the same underlying population (see Eqs 1& 2). If the average response to placebo and psychotherapy controls differs systematically from each other, then this is either due to the fact that the trials sample from different populations or because the control conditions differ in their effects (e.g. because of how much they do or do not protect against expectancy effects).

@@

@stringarisDevelopmentalPathwaysChildhood2014

@@

Table 1 summarises the results from each of the meta-analyses examining sample characteristics at baseline. The summary statistics are provided for each subgroup (i.e. for medication and psychotherapy trials) and the p-value derives from the test for subgroup differences. Full results for each of the sensitivity analyses are included in the Supplementary Materials (Table X - Y).

@@

# Create a flextable object
flextable(df_overall_baseline_results) %>%
  set_caption (autonum = TRUE, "Sample characteristics at baseline across medication and psychotherapy studies") %>%
  bold(part = "header") %>%  # Bold the header row
  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  border_outer(border = small_border) %>%  # Add outer borders
  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>%  # Set table width
  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
  autofit() %>%  # Autofit column widths
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

@@

flextable(df_sites_summary_stats) %>%
  set_caption (autonum = TRUE, "Number of sites across medication and psychotherapy studies", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "all", border = small_border) %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all")

flextable(sites_t_test_stats) %>%
  set_caption (autonum = TRUE, "Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(align = "center", part = "all")

@@

```
There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3. Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).

#### Mean efficacy of psychotherapy versus medication control conditions

@@

flextable(df_mean_coefs_from_sim) %>%
  set_caption (autonum = TRUE, "Summary statistics of the estimated SMDs") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center")

@@

#aggregate_results_overall
flextable(aggregate_results_overall) %>%
  set_caption (autonum = TRUE, "Metaregression results") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(aggregate_results_overall), align = "center")

@@

### Comparing the nature and intensity of control conditions in psychotherapy trials

@@

as_grouped_data(control_summary, groups = "Column") %>% 
  as_flextable(hide_grouplabel = TRUE ) %>% 
  set_caption (autonum = TRUE, "Comparing the intensity of the intervention between active and control arms of psychotherapy studies") %>%
  bold(part = "header") %>%
  bold(i = c(1, 4, 7, 10, 13), j = NULL, bold = TRUE, part = "body") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6, 9, 12), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = 1) %>%  
  bg(bg = "#F2F2F2", part = "header") %>%  
  font(fontname = "Calibri", part = "all")

@@

flextable(control_summary_t_tests) %>%
  set_caption (autonum = TRUE, "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all")

@@

colnames(df_severity_sens)[8] <- paste0(colnames(df_severity_sens)[8], footnote_marker_number(1))

# df_severity_sens %>%
#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
#   kbl(align = "l", caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
#   row_spec(row = 1, bold = T) %>% 
#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
#   column_spec(1, border_right = T) %>% 
#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

colnames(df_gender_sens)[8] <- paste0(colnames(df_gender_sens)[8], footnote_marker_number(1))

# df_gender_sens %>%
#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
#   kbl(align = "l", caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
#   row_spec(row = 1, bold = T) %>% 
#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
#   column_spec(1, border_right = T) %>% 
#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

```{r, warning=FALSE, message = FALSE, echo=FALSE}
# Now age

@@

colnames(df_age_sens)[8] <- paste0(colnames(df_age_sens)[8], footnote_marker_number(1))

# df_age_sens %>%
#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
#   kbl(align = "l", caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
#   row_spec(row = 1, bold = T) %>% 
#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
#   column_spec(1, border_right = T) %>% 
#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))

@@

# Scatter plot cohens d per arm

ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
  geom_point(position = position_jitter(width = 0.2), size = 3) +
  geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
  geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
  geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
  scale_color_manual(values = group_colors) +
  labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
  theme_minimal() +
  theme(legend.position = "none")

@@

# Plot percentage baseline means

ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
  geom_point(position = position_jitter(width = 0.2), size = 3) +
  scale_color_manual(values = group_colors) +
  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
  theme_minimal() +
  theme(legend.position = "none")
```

>>>>

---
title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
author:
  - name: Argyris Stringaris
    email: a.stringaris@ucl.ac.uk
    affiliations: 
        - id: ucl_1
          name: University College London
          department: Divisions of Psychiatry and Psychology and Language Science
          address: 1-19 Torrington Place
          city: London, UK
          state: 
          postal-code: WC1E 7HB
          country: United Kingdom
    attributes:
        corresponding: true
    note: 
  - name: Charlotte Burman
    email: charlotte.burman@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Dayna Bhudia
    email: dayna.bhudia@ucl.ac.uk
    affiliations:
        - ref: ucl_1
  - name: Despina Miliou
    email: dgmiliou@outlook.com.gr
    affiliations:
        - ref: ucl_1
  - name: Giannis Rokas
    email: <rokasgiannis93@gmail.com
    affiliations:
        - ref: ucl_1
  - name: Lucy Foulkes
    email: lucy.foulkes@psych.ox.ac.uk
    affiliations:
        - id: OU
          name: University of Oxford
          department: Experimental Psychology
          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
          city: Oxford
          postal-code: OX2 6GG
          country: United Kingdom
    note:
  - name: Carmen Moreno
    email: cmoreno@hggm.es
    affiliations:
        - id: HGM
          name: Hospital Gregorio Marañón
          department: Department of Psychiatry
          address: 46 C. del Dr. Esquerdo
          city: Madrid
          state:
          postal-code: 28007
          country: Spain
  - name: Samuele Cortese
    email: samuele.cortese@soton.ac.uk
    affiliations:
        - id: soton
          name: University of Southampton
          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
          address: Highfield Campus, Building 44
          city: Southampton
          state:
          postal-code: SO17 1BJ
          country: United Kingdom
  - name: Georgina Krebs
    email: g.krebs@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
keywords: 
  - depression
  - adolescents
  - antidepressants
  - psychotherapy
date: last-modified
prefer-html: true
format: docx
editor: visual
bibliography: "emotion_concepts_paper.bib"
font:
  family: "Calibri"
---

@@

# Introduction

@@

This assumption may be hard to meet. Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication[@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials. Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity. Some of these characteristics, particularly baseline severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.

@@

An inter-related issue concerns the nature of control interventions being used. Control conditions in trials are meant to generate counterfactual conditions (CITE RUBIN et al: **Argyris** how's this? https://us.sagepub.com/sites/default/files/upm-assets/62640_book_item_62640.pdf) to the intervention: what would have been the outcome in an individual had they not received the intervention. This implies that there is a latent distribution of values that represent that counterfactual condition which control arms in trials are meant to approximate. Those latent values of the counterfactual condition should, on average, not be different between psychotherapy and medication trials, provided that the samples are representative of the same underlying population (see Eqs 1& 2). If the average response to placebo and psychotherapy controls differs systematically from each other, then this is either due to the fact that the trials sample from different populations or because the control conditions differ in their effects (e.g. because of how much they do or do not protect against expectancy effects).

@@

@@

Table 1 summarises the results from each of the meta-analyses examining sample characteristics at baseline. The summary statistics are provided for each subgroup (i.e. for medication and psychotherapy trials) and the p-value derives from the test for subgroup differences. Full results for each of the sensitivity analyses are included in the Supplementary Materials (Tables S1 - S3).

@@

flextable(df_overall_baseline_results) %>%
  set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
  bold(part = "header") %>%  # Bold the header row
  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  border_outer(border = small_border) %>%  # Add outer borders
  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>%  # Set table width
  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
  autofit() %>%  # Autofit column widths
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

@@

flextable(df_sites_summary_stats) %>%
  set_caption ("Number of sites across medication and psychotherapy studies", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "all", border = small_border) %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all")

flextable(sites_t_test_stats) %>%
  set_caption ("Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(align = "center", part = "all")

@@

There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3. Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).

## Mean efficacy of psychotherapy versus medication control conditions

@@

flextable(df_mean_coefs_from_sim) %>%
  set_caption ("Summary statistics of the estimated SMDs") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center")

@@

#aggregate_results_overall

flextable(aggregate_results_overall) %>%
  set_caption ("Metaregression results") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(aggregate_results_overall), align = "center")

@@

## Comparing the nature and intensity of control conditions in psychotherapy trials

@@

as_grouped_data(control_summary, groups = "Column") %>% 
  as_flextable(hide_grouplabel = TRUE ) %>% 
  set_caption ("Comparing the intensity of the intervention between active and control arms of psychotherapy studies") %>%
  bold(part = "header") %>%
  bold(i = c(1, 4, 7, 10, 13), j = NULL, bold = TRUE, part = "body") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6, 9, 12), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = 1) %>%  
  bg(bg = "#F2F2F2", part = "header") %>%  
  font(fontname = "Calibri", part = "all")

@@

flextable(control_summary_t_tests) %>%
  set_caption ("Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", style = "Table Caption") %>%
  bold(part = "header") %>%  
  border_outer(border = small_border) %>%  
  hline(part = "header", border = big_border) %>% 
  set_table_properties(width = .75) %>% 
  bg(bg = "#F2F2F2", part = "header") %>%  
  autofit() %>% 
  font(fontname = "Calibri", part = "all") %>%   
  align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all")

@@

df_severity_sens %>%
  mutate_all(~if_else(is.na(.), "", as.character(.)))

flextable(df_severity_sens) %>%
  set_caption(caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials") %>%
  bold(part = "header") %>%  # Bold the header row
  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  border_outer(border = small_border) %>%  # Add outer borders
  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>%  # Set table width
  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
  autofit() %>%  # Autofit column widths
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

@@

df_gender_sens %>%
  mutate_all(~if_else(is.na(.), "", as.character(.)))

flextable(df_gender_sens) %>%
  set_caption(caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials") %>%
  bold(part = "header") %>%  # Bold the header row
  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  border_outer(border = small_border) %>%  # Add outer borders
  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>%  # Set table width
  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
  autofit() %>%  # Autofit column widths
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

# Now age

@@

df_age_sens %>%
  mutate_all(~if_else(is.na(.), "", as.character(.)))

flextable(df_age_sens) %>%
  set_caption(caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials") %>%
  bold(part = "header") %>%  # Bold the header row
  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  border_outer(border = small_border) %>%  # Add outer borders
  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
  hline(part = "header", border = big_border) %>% 
  vline(j = 1, border = big_border) %>% 
  set_table_properties(width = .75) %>%  # Set table width
  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
  autofit() %>%  # Autofit column widths
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")

@@

# # Scatter plot cohens d per arm
# 
# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
#   geom_point(position = position_jitter(width = 0.2), size = 3) +
#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
#   scale_color_manual(values = group_colors) +
#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
#   theme_minimal() +
#   theme(legend.position = "none")

@@

# # Plot percentage baseline means
# 
# ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
#   geom_point(position = position_jitter(width = 0.2), size = 3) +
#   scale_color_manual(values = group_colors) +
#   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
#   theme_minimal() +
#   theme(legend.position = "none")
